### 2018-07-28 Sections/cryptowars.tex
dB, \text->mathrm

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function RSAGenerateKey():
\begin{enumerate}
\item $p$ = randomPrime()
\item $q$ = randomPrime()
\item if($p=q$) goto 1
\item $n = pq$
\item $\lambda = \text{lcm}(p-1,q-1)$
\item $e = \text{coprime}(\lambda) \,\,\text{s.t} \,\,e<\lambda$
\item $d = e^{-1}\,(\text{mod} \, \lambda)$
\item publicKey = $\{n,e\}$
\item privateKey = $\{n,d\}$
\item keyPair = \{publicKey,privateKey\}
\item return(keyPair)
\item $\Box$	
\end{enumerate}
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item $\mathtt{cipertext} = \mathtt{plaintext}^e \, (\text{mod} \, n$)
\item return(ciphertext)
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item $\mathtt{plaintext} = \mathtt{ciphertext}^d \, (\text{mod} \, n)$
\item return(plaintext)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Number-theoretic algorithms based on modular arithmetic for RSA key generation, encryption and decryption.} \label{alg:RSA}
\end{table}

@@

Hash functions are functions that map a long string of arbitrary length to a short, fixed-size string with quasi-random behaviour,
\begin{align}
	f_\text{hash}:\,\{0,1\}^n \to \{0,1\}^m,
\end{align}
for an $n$-bit input and $m$-bit output hash, where $n$ is variable and $m$ is fixed. They are an example of `one-way functions'\index{One-way functions} that are computationally easy to compute in the forward direction, but extremely hard to invert. That is, given a hash, it is computationally difficult to find input strings that map to that value.

@@

In the case of RSA encryption, whose security derives from the believed computational hardness of factorising large numbers, the most efficient known classical algorithm for integer factorisation is the general number field sieve (GNFS)\index{General number field sieve}, with time-complexity,
\begin{align} \label{eq:GNFS_scaling}
	O(\text{exp}[O(1) (\log n)^{\frac{1}{3}} (\log\log n)^{\frac{2}{3}}]),
\end{align}
which scales poorly for large $n$, keeping in mind that present-day implementations of RSA accommodate key lengths of up to 4,096 bits, as for example is implemented by the Pretty Good Privacy (PGP)\index{Pretty Good Privacy} package.

@@

The mining process is based upon the computational hardness of inverting (double) SHA256 hashing\index{Hash functions}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, specifically one which hashes to a value within some range,
\begin{align}
	\epsilon_\text{lower}\leq \text{SHA256}(\text{SHA256}(x_\text{coin})) \leq \epsilon_\text{upper}.
\end{align}
This is slightly weaker than inverting hash functions, but is nonetheless a task that can only be approached via brute-force hashing in the forward direction. This associates computational complexity with the mining process, and hence computational integrity of the money supply, whilst upper bounding the number of unique coins that can exist. This technique is known as `proof-of-work'\index{Proof-of-work}, for associating something of value with proof that certain amounts of computation were required to achieve it\footnote{In future implementations of Blockchain protocols, the proof-of-work required for a given protocol can be arbitrarily manipulated to accommodate for technological advances in computational power, for example via the adoption of quantum computing. The amount of work required to satisfy the constraint grows as we narrow the range \mbox{$\epsilon_\text{upper}-\epsilon_\text{lower}$}, providing us with much leverage to manipulate the complexity of the proof-of-work, and hence the rate of growth in the money supply, equivalently the rate of inflation\index{Inflation rate}.}. This idea was originally borrowed from the Hashcash protocol\index{Hashcash}, where proof-of-work is employed to associate work (and hence monetary value) with sending emails so as to eliminate automated spamming bots.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CVQKD():
\begin{enumerate}
\item Alice chooses two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\text{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\text{mod}),
\end{align}
where $V_\text{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent \comment{I don't get this, Alice is deterministically encoding x+ip, where's the randomness in the choice of basis? Are we adding a randomised phase that puts us into a diagonal basis sometimes, or something like that}
\item \comment{Complete the rest of this}
\end{enumerate}}
\end{mdframed}
\caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n}+\ket{1}^{\otimes n})$
\item $\ket\psi \to (\hat{Z}_\text{speaker})^\text{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\text{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}

>>>>

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function RSAGenerateKey():
\begin{enumerate}
\item $p$ = randomPrime()
\item $q$ = randomPrime()
\item if($p=q$) goto 1
\item $n = pq$
\item $\lambda = \mathrm{lcm}(p-1,q-1)$
\item $e = \mathrm{coprime}(\lambda) \,\,\mathrm{s.t} \,\,e<\lambda$
\item $d = e^{-1}\,(\mathrm{mod} \, \lambda)$
\item publicKey = $\{n,e\}$
\item privateKey = $\{n,d\}$
\item keyPair = \{publicKey,privateKey\}
\item return(keyPair)
\item $\Box$	
\end{enumerate}
function RSAEncrypt(plaintext, publicKey):
\begin{enumerate}
\item $\mathtt{cipertext} = \mathtt{plaintext}^e \, (\mathrm{mod} \, n$)
\item return(ciphertext)
\item $\Box$
\end{enumerate}
function RSADecrypt(ciphertext, privateKey):
\begin{enumerate}
\item $\mathtt{plaintext} = \mathtt{ciphertext}^d \, (\mathrm{mod} \, n)$
\item return(plaintext)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Number-theoretic algorithms based on modular arithmetic for RSA key generation, encryption and decryption.} \label{alg:RSA}
\end{table}

@@

Hash functions are functions that map a long string of arbitrary length to a short, fixed-size string with quasi-random behaviour,
\begin{align}
	f_\mathrm{hash}:\,\{0,1\}^n \to \{0,1\}^m,
\end{align}
for an $n$-bit input and $m$-bit output hash, where $n$ is variable and $m$ is fixed. They are an example of `one-way functions'\index{One-way functions} that are computationally easy to compute in the forward direction, but extremely hard to invert. That is, given a hash, it is computationally difficult to find input strings that map to that value.

@@

In the case of RSA encryption, whose security derives from the believed computational hardness of factorising large numbers, the most efficient known classical algorithm for integer factorisation is the general number field sieve (GNFS)\index{General number field sieve}, with time-complexity,
\begin{align} \label{eq:GNFS_scaling}
	O(\mathrm{exp}[O(1) (\log n)^{\frac{1}{3}} (\log\log n)^{\frac{2}{3}}]),
\end{align}
which scales poorly for large $n$, keeping in mind that present-day implementations of RSA accommodate key lengths of up to 4,096 bits, as for example is implemented by the Pretty Good Privacy (PGP)\index{Pretty Good Privacy} package.

@@

The mining process is based upon the computational hardness of inverting (double) SHA256 hashing\index{Hash functions}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, specifically one which hashes to a value within some range,
\begin{align}
	\epsilon_\mathrm{lower}\leq \mathrm{SHA256}(\mathrm{SHA256}(x_\mathrm{coin})) \leq \epsilon_\mathrm{upper}.
\end{align}
This is slightly weaker than inverting hash functions, but is nonetheless a task that can only be approached via brute-force hashing in the forward direction. This associates computational complexity with the mining process, and hence computational integrity of the money supply, whilst upper bounding the number of unique coins that can exist. This technique is known as `proof-of-work'\index{Proof-of-work}, for associating something of value with proof that certain amounts of computation were required to achieve it\footnote{In future implementations of Blockchain protocols, the proof-of-work required for a given protocol can be arbitrarily manipulated to accommodate for technological advances in computational power, for example via the adoption of quantum computing. The amount of work required to satisfy the constraint grows as we narrow the range \mbox{$\epsilon_\mathrm{upper}-\epsilon_\mathrm{lower}$}, providing us with much leverage to manipulate the complexity of the proof-of-work, and hence the rate of growth in the money supply, equivalently the rate of inflation\index{Inflation rate}.}. This idea was originally borrowed from the Hashcash protocol\index{Hashcash}, where proof-of-work is employed to associate work (and hence monetary value) with sending emails so as to eliminate automated spamming bots.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function CVQKD():
\begin{enumerate}
\item Alice chooses two Gaussian-distributed random numbers with mean zero,
\begin{align}
x_A &= \mathcal{N}(0,V_\mathrm{mod}),\nonumber \\
p_A &= \mathcal{N}(0,V_\mathrm{mod}),
\end{align}
where $V_\mathrm{mod}$ is the modulation variance\index{Modulation variance}.
\item Alice prepares the coherent state,
\begin{align}
\ket\alpha = \ket{x_A+ip_A}.	
\end{align}
\item Alice transmits $\ket\alpha$ to Bob.
\item Bob randomly measures either $\hat{x}$ or $\hat{p}$ using homodyne detection.
\item Alice and Bob use classical communication to determine for which transmissions their preparation and measurement were consistent \comment{I don't get this, Alice is deterministically encoding x+ip, where's the randomness in the choice of basis? Are we adding a randomised phase that puts us into a diagonal basis sometimes, or something like that}
\item \comment{Complete the rest of this}
\end{enumerate}}
\end{mdframed}
\caption{CV QKD protocol using coherent states, encoded in the quadrature basis.}\label{alg:cv_qkd}
\end{table}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QuantumAnonymousBroadcasting(message, speaker):
\begin{enumerate}
\item $\ket\psi = \frac{1}{\sqrt{2}}(\ket{0}^{\otimes n}+\ket{1}^{\otimes n})$
\item $\ket\psi \to (\hat{Z}_\mathrm{speaker})^\mathrm{message}\ket\psi$
\item for(i$\in$users) \{
	\setlength{\itemindent}{.2in}
\item outcome$_i$ = measureInXBasis($\ket\psi_\mathrm{i}$)
\setlength{\itemindent}{0in}
\item \}
\item parity = $\sum_i$ outcome$_i$\,(mod\,2)
\item return(parity)
\item $\Box$
\end{enumerate}
}
\end{mdframed}
\caption{Protocol for quantum anonymous broadcasting. The GHZ state is distributed in advance, one qubit per user. The measurement outcomes are classically broadcast without encryption. The final parity of the classical measurements reflects the message bit without identifying the speaker.} \label{alg:QAB}
\end{table}
